Hierarchically Supervised Latent Dirichlet Allocation

### 2011-06-02 paper/experiments.tex
figure placement and captions

The task of automatic ICD-9 coding has been investigated in the clinical
domain.  Methods range from manual
rules to online learning~\cite{Crammer2007,Goldstein2007,Farkas2008}.
Other work had leveraged larger datasets and experimented with K-nearest
neighbor, Naive Bayes, support vector machines, Bayesian Ridge Regression, as
well as simple keyword mappings, all with promising
results~\cite{LarkeyCroft95,RibeiroNeto2001,PakhomovEtAl06,Ruch2008,Lita2008}.

@@

\begin{figure}%[htbp]
\begin{center}
%\subfloat[][\label{fig:1a}]{\includegraphics[width=.49\textwidth]{figs/amazon_pred_varying_mu}}
\subfigure[][]{\label{fig:1a}\includegraphics[width=.49\textwidth]{figs/clin_pred_varying_mu}}
%\subfloat[][\label{fig:1c}]{\includegraphics[width=.49\textwidth]{figs/sens_comparison_leafs}}
\subfigure[][]{\label{fig:1b}\includegraphics[width=.49\textwidth]{figs/amazon_pred_varying_mu}}
\caption{Out-of-sample ICD-9 code prediction from patient free-text discharge records 
(\subref{fig:1b}). Out-of-sample Amazon product category predictions from 
product free-text descriptions (\subref{fig:1b}). In both figures, solid is 
HSLDA, dashed are independent regressors + sLDA (hierarchical 
constraints on labels ignored), and dotted is HSLDA fit by running LDA first then running 
tree-conditional regressions.}
\label{fig:main_results}
\end{center}
\end{figure}

\begin{figure}[t]
%tbp] %  figure placement: here, top, bottom, or page
 \centering \includegraphics[scale=0.4]{figs/ROC_comparison_leafs} \caption{ROC Curve for clinical data}
\label{fig:clinical_roc} 
\end{figure}

>>>>

The task of automatic ICD-9 coding has been investigated in the clinical
domain.  Methods range from manual
rules to online learning~\cite{Crammer2007,Goldstein2007,Farkas2008}.
Other work had leveraged larger datasets and experimented with K-nearest
neighbor, Naive Bayes, support vector machines, Bayesian Ridge Regression, as
well as simple keyword mappings, all with promising
results~\cite{LarkeyCroft95,RibeiroNeto2001,PakhomovEtAl06,Lita2008}.%Ruch2008 omitted

@@

\begin{figure}%[htbp]
\begin{center}
%\subfloat[][\label{fig:1a}]{\includegraphics[width=.49\textwidth]{figs/amazon_pred_varying_mu}}
\subfigure[][]{\label{fig:1a}\includegraphics[width=.49\textwidth]{figs/clin_pred_varying_mu}}
%\subfloat[][\label{fig:1c}]{\includegraphics[width=.49\textwidth]{figs/sens_comparison_leafs}}
\subfigure[][]{\label{fig:1b}\includegraphics[width=.49\textwidth]{figs/amazon_pred_varying_mu}}
\subfigure[][]{\label{fig:clinical_roc}\includegraphics[scale=0.4]{figs/ROC_comparison_leafs}}
\caption{ROC curves for out-of-sample ICD-9 code prediction from patient free-text discharge records 
(\subref{fig:1a},\subref{fig:clinical_roc}). ROC curve for out-of-sample Amazon product category predictions from 
product free-text descriptions \subref{fig:1b}. Figures \subref{fig:1a} and \subref{fig:1b} are a function 
of the prior means of the regression parameters. Figure \subref{fig:clinical_roc} is a function of auxiliary variable threshold. In all figures, solid is 
HSLDA, dashed are independent regressors + sLDA (hierarchical 
constraints on labels ignored), and dotted is HSLDA fit by running LDA first then running 
tree-conditional regressions.}
\label{fig:main_results}
\end{center}
\end{figure}

%\begin{figure}[t]
%%tbp] %  figure placement: here, top, bottom, or page
% \centering \includegraphics[scale=0.4]{figs/ROC_comparison_leafs} \caption{ROC curve for Out-of-sample ICD-9 code predictions.}
%\label{fig:clinical_roc} 
%\end{figure}
